---
title: "STAT2011 COMP_ASM"
author: "Timothy"
date: "5/26/2021"
output:
  html_document:
    df_print: paged
---

# Question 1.
(a).
```{r}
set.seed(200)
n = 10
Times = (10)^4

# By row
a = replicate(Times, sum(sample(1:6, n, replace = TRUE)) >= 40)
mean(a)
```
The approximate probability is **0.1998**

(b).
```{r}
E_Y = 35
VAR_Y = 175/6
P = 1 - pnorm(40, E_Y, sqrt(VAR_Y))
round(P,4)
```
The Central Limit Theorem approximation of the probability of winning the game without continuity correction is 0.1773. This is lower than the Monte Carlo approximation obtained in (a).


(c).

```{r}
1 - pnorm(39.5, E_Y, sqrt(VAR_Y))
```

The Central Limit Theorem approximation of the probability of winning the game with continuity correction is 0.2024. This is slightly higher than the Monte Carlo approximation obtained in (a).


# Question 2.

(a)

```{r}
x = 0:4
FREQ = c(130, 133, 49, 7, 1)
xbar = sum(x*FREQ) / sum(FREQ)
phat = xbar / 4
phat
```

The estimate of $p$ using the method of moments is **0.2**.


(b)
```{r}
e = round(dbinom(x, 4, phat) * sum(FREQ))
e
```

(c)
```{r}
sr = (FREQ - e) / sqrt(e)
abs(sr)
```

All SR in absolute are less than 2, so the fitted binomial model is a good model for the data.


# Question 3.
(a)
```{r}
set.seed(100)


n = 25
mu = 3
sigma = 1.5

x = rnorm(n, mu, sigma)

mean(x) + c(Lower = -1, Upper = 1) * qnorm(0.975) * sigma/sqrt(n)
```

(b)
```{r}
m = 20

x.mat = matrix(rnorm(n*m, mu, sigma), n)
xbar.vec = colMeans(x.mat)
lower = xbar.vec - qnorm(0.975) * sigma/sqrt(n)
upper = xbar.vec + qnorm(0.975) * sigma/sqrt(n) 
sum((lower <= mu) & (mu <= upper))
```

The number of these 20 intervals contain the true mean $\mu = 3$ is 19.


# Question 4.
(a)
```{r}
set.seed(100)
size = 30
lambda = 2
N = 1000


xbar = replicate(N, mean(rexp(size, lambda)))
hist(xbar, 30, prob = TRUE)
```

(b)
```{r}

hist(xbar, 30, prob = TRUE)

curve(dnorm(x, 1/lambda, sqrt(1/lambda^2/n)), add = TRUE, col = 'blue')
```

We can see the histogram of these 1000 means is roughly consistent with a normal density curve, so the Central Limit Theorem gives a good approximation for the distribution of the means.


